### 2024-02-07 README.Rmd
use saved png for output of brms model
correct sourcing of image from vignette/articles folder, labelling of joined constituencies

```{r}
st_bridges(df = uk_election|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2)  |> 
  st_manual_join_nb("Gower","St Ives") |> 
  st_quickmap_nb()
```

@@

Further information and worked examples are available in the vignettes which can be found [here](https://horankev.github.io/sfislands/).

>>>>

```{r}
st_bridges(df = uk_election|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2)  |> 
  st_manual_join_nb("Gower","St Ives") |> 
  st_quickmap_nb() + 
  geom_sf_label(data=uk_election|> filter(constituency_name %in% c("Gower","St Ives")),
                aes(label=constituency_name),nudge_x = -30000)
```

@@

Further information and worked examples are available in the this [article](https://horankev.github.io/sfislands/).
